Redundant calibration as a complex optimization problem

### 2016-12-06 paper.tex
added some text to sparsity section

We can now use the sparsity factor to compute the order of the computational cost of inverting $\bH$ as follows:
\begin{align}
P^{c} &= (1 - \gamma)P^2\\
c &= \log_{P}(1 - \gamma) + 2 & c_{\infty} &= \lim_{N\rightarrow \infty} c = 2
\end{align}

Asymptotically the computational cost of inverting $\bH$ is $O(P^2)$. However, the computational cost converges 
very slowly to its asymptotic value, and in general is equal to $O(P^{c})$, where $c \sim 1.7$ if a Hexagonal geometric layout is employed.

>>>>

We can now use the sparsity factor to compute the order of the computational cost of inverting $\bH$ with
\begin{equation}
P^{c} = (1 - \gamma)P^2.
\end{equation}
Solving for $c$ we obtain
\begin{align}
c &= \log_{P}(1 - \gamma) + 2 & c_{\infty} &= \lim_{N\rightarrow \infty} c = 2.
\end{align}
Asymptotically the computational cost of inverting $\bH$ is $O(P^2)$. However, the computational cost converges 
very slowly to its asymptotic value, and in general is equal to $O(P^{c})$, where $c \sim 1.7$ if a Hexagonal geometric layout is employed.
